---
title: "EPIC Function Vignette"
author: "Jacob Rosen"
date: "2024-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Guide to import and use the NASA DSCOVR: EPIC API

### Step 1: Import the function script   
In order to call the function, we must import the R script where the function is defined ("epic_wrapper.R").    

```{r, echo=FALSE}

source("../epic_wrapper.R")

```    
      
If you are in another directory, you must also add the file path where this script is located in addition to the file name. 

### Step 2: Call the "get_image_urls(type, date)" function    
Once the script has been successfully imported, call the get_image_urls() function and pass the type of images you want to view and the date. 

**Type:** 
If no type is provided the default will be 'natural'. Other types include 'enhanced', 'aerosol', and 'cloud'. 

**Date:**
If no date is provided the default date is the most recent date with available images. Format should be 'YYYY-MM-DD'.

The function returns a list of urls to access the images on a browser.

```{r}
images <- get_image_urls('natural', '2024-01-01')
```

This is the first item from the images list:

<img src="`r images[1]`" alt="Image from EPIC API for 2024-01-01" width="200"/>

Here are examples of the other types of images

```{r}
images_enhanced <- get_image_urls('enhanced', '2024-01-01')
images_aerosol <- get_image_urls('aerosol', '2024-01-01')
images_cloud <- get_image_urls('cloud', '2024-01-01')
```

#### Enhanced

<img src="`r images_enhanced[1]`" alt="Enhanced image from EPIC API for 2024-01-01" width="200"/>

#### Aerosol

<img src="`r images_aerosol[1]`" alt="Aerosol image from EPIC API for 2024-01-01" width="200"/>

#### Cloud

<img src="`r images_cloud[1]`" alt="Cloud image from EPIC API for 2024-01-01" width="200"/>


### Step 3: Call the "plot_centroids(type, date)" function    
We can get an idea of the scope of each image taken on a given day by plotting the centroids of each image in the set. Call the plot_centroids() function with the same parameters as before.

```{r, fig.width=7}
plot_centroids('natural', '2024-01-01')
```

Image epic_1b_20240101024318 is taken with a centroid over Australia:

<img src="`r images[2]`" alt="epic_1b_20240101024318" width="200"/>

Image epic_1b_20240101151935 is taken with a centroid over South America on the same day:

<img src="`r images[9]`" alt="epic_1b_20240101151935" width="200"/>