---
title: "NEO Function Vignette"
author: "Dhun Sheth"
date: "2024-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Guide to import and use the NASA NEO API

### Step 1: Import the function script   
In order to call the function, we must import the R script where the function is defined ("neo_function_wrapper.R").    

```{r}

source("../neo_function_wrapper.R")

```    
      
If you are in another directory, you must also add the file path where this script is located in addition to the file name. 

### Step 2: Call the "get_neo(start_date, end_date)" function    
Once the script has been successfully imported, call the get_neo() function and pass the start and end date.   
     
**Note:** Can only call max 7 days worth of data, so an error will be encountered if the difference between start/end date is more than 7.     

**Format of Date:** YYYY-MM-DD

```{r, fig.width=10}

a <- get_neo('2023-12-20','2023-12-27')

```


Example of error if difference in date is longer than 7 days.

```{r}

a <- get_neo('2023-12-20','2023-12-30')
print(a)

```


### Step 3: Conclusion     
All data is returned by the function, so if additional analysis is needed, it can be accessed by calling `a$data`.     

In addition, asteroid specific information can be retrieved via `a$data$links`.
