---
title: "Rover Images Vignette"
author: "Tim Pulfer"
date: "2024-02-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Guide to import and use the NASA Rover API

### Step 1: Import the function script   
In order to call the function, we must import the R script where the function is defined ("rover_images_wrapper_module").    
```{r}
source("../rover_images_wrapper_module.R")
```

If you are in another directory, you must also add the file path where this script is located in addition to the file name.

### Step 2: Call the "get_mars_rover_image_url(rover, camera, date)" function    

**Format of camera:** FHAZ, RHAZ, MAST, CHEMCAM, MAHLI, MARDI, NAVCAM. For "opportunity" and "spirit": FHAZ, RHAZ, NAVCAM, PANCAM, MINITES.

**Format of rover:** "curiosity", "opportunity", and "spirit"

**Format of date:** YYYY-MM-DD

```{r}
img_link <- get_mars_rover_image_url("curiosity", "fhaz", "2023-01-01")
```

### Step 3: Conclusion     
This function will return a hyperlink to the requested image. Copy/paste this URL into a web browser to see the image.

